Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-02-01 CAV2018/paper.tex
dot

We will assume, for the purposes of this analysis, that the domain of the
ADC is that of the digital controller (i.e, the quantizer includes a digital
gain added in the code resulting in $\mathbb{R}_{\langle A
\rangle}=\mathbb{R}_{\langle C \rangle}$).  The process of quantization in
the DAC is similar except that it is calculating $\mathcal{F}_{\langle
D\rangle} (\mathcal{F}_{\langle C \rangle} (x)) $.  If these domains are the
same ($\mathbb{R}_{\langle D \rangle}=\mathbb{R}_{\langle C \rangle}$), or
if the DAC resolution in higher than the ADCs ($\mathbb{R}_{\langle D
\rangle}\supseteq\mathbb{R}_{\langle C \rangle}$), then the DAC quantization
error is equal to zero.  From the above equations we can now define the ADC
and DAC quantization noises ${\nu_1}_k \in [-\frac{q_a}{2}, \frac{q_a}{2}]$
and ${\nu_2}_k \in [-\frac{q_d}{2}, \frac{q_d}{2}]$, where given the above
assumptions $q_d=q_a=q_c$.  This is illustrated in Figure
\ref{fig:observersystem} where $Q_1$ is the quantizer of the ADC and $Q_2$
the quantizer for the DAC.  These bounds hold irrespective of whether the
noise is correlated, hence we may use them to over-approximate the noise
effect on the state space progression over time.  The resulting dynamics are
%
\begin{align*}
%\label{eq:pre_quantization}
\vec{x}_{k+1} = \mat{A}_d\vec{x}_k+\mat{B}_d({u}_k+{{\nu}_2}_k), \quad u_k = -\mat{K}\vec{x}_{k}+{{\nu}_1}_k, 
\end{align*}
%
which result in the following closed-loop dynamics:
%
\begin{align*}
%\label{eq:quantization}
\vec{x}_{k+1} &= (\mat{A}_d-\mat{B}_d\mat{K}_d) \vec{x}_k+\mat{B}_d{{\nu}_2}_k +{{\nu}_1}_k \,. 
\end{align*}

>>>>

We will assume, for the purposes of this analysis, that the domain of the
ADC is that of the digital controller (i.e., the quantizer includes a digital
gain added in the code resulting in $\mathbb{R}_{\langle A
\rangle}=\mathbb{R}_{\langle C \rangle}$).  The process of quantization in
the DAC is similar except that it is calculating $\mathcal{F}_{\langle
D\rangle} (\mathcal{F}_{\langle C \rangle} (x)) $.  If these domains are the
same ($\mathbb{R}_{\langle D \rangle}=\mathbb{R}_{\langle C \rangle}$), or
if the DAC resolution in higher than the ADCs ($\mathbb{R}_{\langle D
\rangle}\supseteq\mathbb{R}_{\langle C \rangle}$), then the DAC quantization
error is equal to zero.  From the above equations we can now define the ADC
and DAC quantization noises ${\nu_1}_k \in [-\frac{q_a}{2}, \frac{q_a}{2}]$
and ${\nu_2}_k \in [-\frac{q_d}{2}, \frac{q_d}{2}]$, where given the above
assumptions $q_d=q_a=q_c$.  This is illustrated in Figure
\ref{fig:observersystem} where $Q_1$ is the quantizer of the ADC and $Q_2$
the quantizer for the DAC.  These bounds hold irrespective of whether the
noise is correlated, hence we may use them to over-approximate the noise
effect on the state space progression over time.  The resulting dynamics are
%
\begin{align*}
%\label{eq:pre_quantization}
\vec{x}_{k+1} = \mat{A}_d\vec{x}_k+\mat{B}_d({u}_k+{{\nu}_2}_k), \quad u_k = -\mat{K}\vec{x}_{k}+{{\nu}_1}_k, 
\end{align*}
%
which result in the following closed-loop dynamics:
%
\begin{align*}
%\label{eq:quantization}
\vec{x}_{k+1} &= (\mat{A}_d-\mat{B}_d\mat{K}_d) \vec{x}_k+\mat{B}_d{{\nu}_2}_k +{{\nu}_1}_k \,. 
\end{align*}
